---
format: typst
---

# Medical Insurance Cost Dataset (Kaggle)

[Link](https://www.kaggle.com/datasets/mirichoi0218/insurance)
[file](data/insurance.csv)

- 1338 observations
- 7 variables
- response: `charges`


# Diamonds (ggplot2)

[link](https://ggplot2.tidyverse.org/reference/diamonds.html)


```{r}
library(ggplot2)
data(diamonds)
```

- 53940 observations
- 10 variables
- response: `price`




# Tips (reshape2)

[link](https://rdrr.io/cran/reshape2/man/tips.html)
[file](https://github.com/mwaskom/seaborn-data/blob/master/tips.csv)


```{r}
library(reshape2)
data(tips)
```


- 244 observations
- 7 variables
- response: `tip`


# Wage (ISLR)

[link](https://cran.r-project.org/web/packages/ISLR2/refman/ISLR2.html#Wage)


```{r}
#| warning: false
library(ISLR)
data(Wage)
```

- Wage and other data for a group of 3000 male workers in the Mid-Atlantic region.
- 3000 observations
- 11 variables
- response: `wage`


# College (ISLR)

[link](https://cran.r-project.org/web/packages/ISLR2/refman/ISLR2.html#College)


```{r}
#| warning: false
library(ISLR)
data(College)
```


- Statistics for a large number of US Colleges from the 1995 issue of US News and World Report.
- 777 observations
- 18 variables
- response: typical chosse `Outstate` Out-of-state tuition

# Hitters (ISLR)



[link](https://cran.r-project.org/web/packages/ISLR2/refman/ISLR2.html#Hitters)

```{r}
#| warning: false
library(ISLR)
data(Hitters)
```


- MLB baseball data 1986-1987
- 322 observations
- 20 variables
- response: `Salary`


# Carseats (ISLR)

[link](https://cran.r-project.org/web/packages/ISLR2/refman/ISLR2.html#Carseats)


```{r}
#| warning: false
library(ISLR)
data(Carseats)
```

- A simulated data set containing sales of child car seats at 400 different stores.
- 400 obseravations
- 11 variables
- response: `Sales`



# Student Performance (UCI)

[link](https://archive.ics.uci.edu/dataset/320/student+performance)

[math](data/student-mat.csv)

[por](data/student-por.csv)

[combine](data/student-combine.csv)

The combined dataset is gotten by the following code.
```{r}
#| eval: false
d1 <- read.table("student-mat.csv", sep = ";", header = TRUE)
d2 <- read.table("student-por.csv", sep = ";", header = TRUE)

d3 <- merge(d1, d2, by = c("school", "sex", "age", "address", "famsize", "Pstatus", "Medu", "Fedu", "Mjob", "Fjob", "reason", "nursery", "internet"))
```

- This data approach student achievement in secondary education of two Portuguese schools. 
- 649 observations in por, 395 in math, and 382 in common
- The common students can be identified by searching for identical attributes that characterize each student, as shown in the above code.
- 30 variables (with 3 additional grade variables)
- response: `G3` final grade


# heart disease (UCI)

[link](https://archive.ics.uci.edu/dataset/45/heart+disease)