

# Notes

This document lists UCI datasets that are potentially useful for regression projects.  
For each dataset below, I include:

- the UCI webpage link,
- an R code chunk to import the dataset,
- basic information such as number of variables, number of observations, response variable, and topic.

Most import examples use the `{ucimlrepo}` package, which can fetch datasets directly from the UCI Machine Learning Repository from within R.

```{r}
#| warning: false
# install.packages("ucimlrepo")
library(ucimlrepo)
```

# Clean datasets

## Student Performance

Webpage: <https://archive.ics.uci.edu/dataset/320/student+performance>

```{r}
student_performance <- fetch_ucirepo(id = 320)
student_performance_data <- student_performance$data$original

dim(student_performance_data)
head(student_performance_data)
```


- **Number of features:** 30
- **Number of targets:** 3
- **Number of observations:** 649 
- **Response variable:** official targets are `G1`, `G2`, and `G3`; for regression, `G3` is the usual choice
- **Topic:** student achievement in secondary education

## Bike Sharing

Webpage: <https://archive.ics.uci.edu/ml/datasets/bike+sharing+dataset>

```{r}
bike_sharing <- fetch_ucirepo(id = 275)
bike_sharing_data <- bike_sharing$data$original

dim(bike_sharing_data)
head(bike_sharing_data)
```

- **Number of features:** 13
- **Number of targets:** 3
- **Number of observations:** 17,379 for the hourly data
- **Response variable:** official targets are `casual`, `registered`, and `cnt`; `cnt` is the usual choice
- **Topic:** bicycle rental demand with weather and seasonal information

## Auto MPG

Webpage: <https://archive.ics.uci.edu/ml/datasets/auto+mpg>

```{r}
auto_mpg <- fetch_ucirepo(id = 9)
auto_mpg_data <- auto_mpg$data$original

dim(auto_mpg_data)
head(auto_mpg_data)
```

- **Number of features:** 7
- **Number of targets:** 1
- **Number of observations:** 398
- **Response variable:** `mpg`
- **Topic:** fuel economy of automobiles

## Wine Quality

Webpage: <https://archive.ics.uci.edu/dataset/186/wine+quality>

```{r}
wine_quality <- fetch_ucirepo(id = 186)
wine_quality_data <- wine_quality$data$original

dim(wine_quality_data)
head(wine_quality_data)
```

- **Number of features:** 12
- **Number of targets:** 1
- **Number of observations:** 6,497 combined across red and white wine data.
- **Response variable:** `quality`
- **Topic:** predicting wine quality from physicochemical measurements


## Heart Disease

Webpage: <https://archive.ics.uci.edu/dataset/45/heart+disease>

```{r}
heart_disease <- fetch_ucirepo(id = 45)
heart_disease_data <- heart_disease$data$original

dim(heart_disease_data)
head(heart_disease_data)
```

- **Number of features:** 13
- **Number of targets:** 1
- **Number of observations:** 303 for the Cleveland subset typically used in teaching
- **Response variable:** official target is `num`, and treat it as a severity score (while the orginal num is only integer).
- **Topic:** clinical measurements related to heart disease

## Forest Fires

Webpage: <https://archive.ics.uci.edu/dataset/162/forest+fires>

```{r}
forest_fires <- fetch_ucirepo(id = 162)
forest_fires_data <- forest_fires$data$original

dim(forest_fires_data)
head(forest_fires_data)
```

- **Number of features:** 12
- **Number of targets:** 1
- **Number of observations:** 517
- **Response variable:** `area`
- **Topic:** predicting burned area of forest fires using weather and fire indices

## Energy Efficiency

Webpage: <https://archive.ics.uci.edu/dataset/242/energy+efficiency>

```{r}
energy_efficiency <- fetch_ucirepo(id = 242)
energy_efficiency_data <- energy_efficiency$data$original

dim(energy_efficiency_data)
head(energy_efficiency_data)
```

- **Number of features:** 8
- **Number of targets:** 2
- **Number of observations:** 768
- **Response variable:** official targets are `Y1` and `Y2`
- **Topic:** building energy efficiency

## Airfoil Self-Noise

Webpage: <https://archive.ics.uci.edu/dataset/291/airfoil+self+noise>

```{r}
airfoil_self_noise <- fetch_ucirepo(id = 291)
airfoil_self_noise_data <- airfoil_self_noise$data$original

dim(airfoil_self_noise_data)
head(airfoil_self_noise_data)
```

- **Number of features:** 5
- **Number of targets:** 1
- **Number of observations:** 1,503
- **Response variable:** `scaled-sound-pressure`
- **Topic:** aerodynamic and acoustic properties of airfoils

<!-- 
## Yacht Hydrodynamics

Webpage: <https://archive.ics.uci.edu/dataset/243/yacht+hydrodynamics>

```{r}
#| eval: false
yacht_hydrodynamics <- fetch_ucirepo(id = 243)
yacht_hydrodynamics_data <- yacht_hydrodynamics$data$original

dim(yacht_hydrodynamics_data)
head(yacht_hydrodynamics_data)
```

- **Number of features:** 6
- **Number of targets:** 1
- **Number of observations:** 308
- **Response variable:** residuary resistance per unit weight of displacement
- **Topic:** yacht design and hydrodynamic resistance -->

## Parkinsons Telemonitoring

Webpage: <https://archive.ics.uci.edu/dataset/189/parkinsons+telemonitoring>

```{r}
parkinsons_telemonitoring <- fetch_ucirepo(id = 189)
parkinsons_telemonitoring_data <- parkinsons_telemonitoring$data$original

dim(parkinsons_telemonitoring_data)
head(parkinsons_telemonitoring_data)
```

- **Number of features:** 19
- **Number of targets:** 2
- **Number of observations:** 5,875
- **Response variable:** official targets are `motor_UPDRS` and `total_UPDRS`
- **Topic:** remote monitoring of Parkinson's disease symptoms from voice measures

## Abalone

Webpage: <https://archive.ics.uci.edu/dataset/1/abalone>

```{r}
abalone <- fetch_ucirepo(id = 1)
abalone_data <- abalone$data$original

dim(abalone_data)
head(abalone_data)
```

- **Number of features:** 8
- **Number of targets:** 1
- **Number of observations:** 4,177
- **Response variable:** `Rings`
- **Topic:** predicting abalone age from physical measurements

## Concrete Compressive Strength

Webpage: <https://archive.ics.uci.edu/dataset/165/concrete+compressive+strength>

```{r}
concrete_strength <- fetch_ucirepo(id = 165)
concrete_strength_data <- concrete_strength$data$original

dim(concrete_strength_data)
head(concrete_strength_data)
```

- **Number of features:** 8
- **Number of targets:** 1
- **Number of observations:** 1,030
- **Response variable:** `Concrete compressive strength`
- **Topic:** civil engineering and material strength

## Electrical Grid Stability Simulated Data

Webpage: <https://archive.ics.uci.edu/dataset/471/electrical+grid+stability+simulated+data>

```{r}
electrical_grid_stability <- fetch_ucirepo(id = 471)
electrical_grid_stability_data <- electrical_grid_stability$data$original

dim(electrical_grid_stability_data)
head(electrical_grid_stability_data)
```

- **Number of features:** 12
- **Number of targets:** 2
- **Number of observations:** 10,000
- **Response variable:** official targets are `stab` and `stabf`; for regression, use `stab`
- **Topic:** simulated electrical grid stability

## Seoul Bike Sharing Demand

Webpage: <https://archive.ics.uci.edu/dataset/560/seoul+bike+sharing+demand>

```{r}
seoul_bike_sharing <- fetch_ucirepo(id = 560)
seoul_bike_sharing_data <- seoul_bike_sharing$data$original

dim(seoul_bike_sharing_data)
head(seoul_bike_sharing_data)
```

- **Number of features:** 13
- **Number of targets:** 1
- **Number of observations:** 8,760
- **Response variable:** `Rented Bike Count`
- **Topic:** urban bike rental demand with weather and seasonal information

## Gas Turbine CO and NOx Emission Data Set

Webpage: <https://archive.ics.uci.edu/dataset/551/gas+turbine+co+and+nox+emission+data+set>

```{r}
gas_turbine <- fetch_ucirepo(id = 551)
gas_turbine_data <- gas_turbine$data$original

dim(gas_turbine_data)
head(gas_turbine_data)
```

- **Number of variables:** 10
- **Number of observations:** 36,733
- **Response variable:** official targets are `CO` and `NOX`
- **Topic:** gas turbine emissions and sensor measurements

## Superconductivity

Webpage: <https://archive.ics.uci.edu/dataset/464/superconductivty+data>

```{r}
superconductivity <- fetch_ucirepo(id = 464)
superconductivity_data <- superconductivity$data$original

dim(superconductivity_data)
head(superconductivity_data)
```

- **Number of features:** 81
- **Number of targets:** 1
- **Number of observations:** 21,263
- **Response variable:** `critical_temp`
- **Topic:** materials science and superconductivity

## Appliances Energy Prediction

Webpage: <https://archive.ics.uci.edu/dataset/374/appliances+energy+prediction>

```{r}
appliances_energy <- fetch_ucirepo(id = 374)
appliances_energy_data <- appliances_energy$data$original

dim(appliances_energy_data)
head(appliances_energy_data)
```

- **Number of features:** 28
- **Number of targets:** 1
- **Number of observations:** 19,735
- **Response variable:** `Appliances`
- **Topic:** household energy use prediction

# Datasets that need a little preprocessing

## Adult

Webpage: <https://archive.ics.uci.edu/dataset/2/adult>

```{r}
adult <- fetch_ucirepo(id = 2)
adult_data <- adult$data$original

dim(adult_data)
head(adult_data)
```

- **Number of features:** 14
- **Number of targets:** 1
- **Number of observations:** 48,842
- **Response variable:** if you want regression, a workable quantitative outcome is `hours-per-week`
- **Topic:** census-style demographic and employment data
- **Missing-data handling:** convert `?` placeholders to `NA`
- **Parsing / encoding:** one-hot encode categorical predictors such as work class, education, marital status, occupation, relationship, race, sex, and native country
- **Other preparation:** remove or redefine the original classification target if it is not part of the regression task

<!-- ## Bank Marketing

Webpage: <https://archive.ics.uci.edu/dataset/222/bank+marketing>

```{r}
#| eval: false
bank_marketing <- fetch_ucirepo(id = 222)
bank_marketing_data <- bank_marketing$data$original

dim(bank_marketing_data)
head(bank_marketing_data)
```

- **Number of features:** 16
- **Number of targets:** 1
- **Number of observations:** 45,211
- **Response variable:** official target is `y`; for regression, users sometimes instead model a quantitative field such as `balance`
- **Topic:** direct marketing campaigns by a Portuguese banking institution
- **Preprocessing needed:** remove or carefully handle the campaign outcome variable `y` if it is not being modeled
- **Preprocessing needed:** encode categorical fields such as job, marital status, education, contact type, month, and poutcome
- **Preprocessing needed:** check for skewness in `balance`, `duration`, and campaign-count variables and transform if needed -->

<!-- ## Online Retail

Webpage: <https://archive.ics.uci.edu/dataset/352/online+retail>

```{r}
#| eval: false
online_retail <- fetch_ucirepo(id = 352)
online_retail_data <- online_retail$data$original

dim(online_retail_data)
head(online_retail_data)
```

- **Number of variables:** 8
- **Number of observations:** 541,909
- **Response variable:** a quantitative choice is `UnitPrice`
- **Topic:** online retail transactions
- **Preprocessing needed:** parse `InvoiceDate` as a date-time variable
- **Preprocessing needed:** remove cancellations and returns, typically identified by invoice codes beginning with `C` or by negative quantities
- **Preprocessing needed:** decide how to handle missing `CustomerID`
- **Preprocessing needed:** encode `Country` and engineer transaction-level or customer-level features if modeling beyond raw line items -->

<!-- ## Car Evaluation

Webpage: <https://archive.ics.uci.edu/dataset/19/car+evaluation>

```{r}
#| eval: false
car_evaluation <- fetch_ucirepo(id = 19)
car_evaluation_data <- car_evaluation$data$original

dim(car_evaluation_data)
head(car_evaluation_data)
```

- **Number of features:** 6
- **Number of targets:** 1
- **Number of observations:** 1,728
- **Response variable:** this is mainly a classification dataset; if you use it for regression, you would need to create an ordinal or numeric response yourself
- **Topic:** car acceptability evaluation
- **Preprocessing needed:** create a numeric or ordinal response from the categorical acceptability label
- **Preprocessing needed:** encode all predictors, which are categorical and ordinal
- **Preprocessing needed:** preserve ordinal structure for variables such as buying price, maintenance cost, safety, luggage boot size, and number of persons -->

## Air Quality

Webpage: <https://archive.ics.uci.edu/dataset/360/air+quality>

```{r}
air_quality <- fetch_ucirepo(id = 360)
air_quality_data <- air_quality$data$original

dim(air_quality_data)
head(air_quality_data)
```

- **Number of features:** 14
- **Number of targets:** 1
- **Number of observations:** 9,357
- **Response variable:** a reasonable regression target is one ground-truth pollutant measurement, such as `CO(GT)`
- **Topic:** air pollution measurements from gas sensors
- **Missing-data handling:** convert the original missing-value code, commonly `-200`, to `NA`
- **Parsing / encoding:** parse and combine the date and time fields into a usable timestamp
- **Other preparation:** after choosing one `(GT)` pollutant as the target, drop the other `(GT)` pollutant columns and keep the sensor, weather, and time-based variables as predictors




<!-- 
## Individual Household Electric Power Consumption

Webpage: <https://archive.ics.uci.edu/dataset/235/individual+household+electric+power+consumption>

```{r}
#| eval: false
household_power <- fetch_ucirepo(id = 235)
household_power_data <- household_power$data$original

dim(household_power_data)
head(household_power_data)
```

- **Number of features:** 9
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** 2,075,259
- **Response variable:** a clear regression target is `Global_active_power`, the household's minute-level active power consumption
- **Topic:** household electricity consumption over time
- **Missing-data handling:** convert blank measurement fields to `NA`; the UCI page notes that about 1.25% of the measurement rows have missing values
- **Parsing / encoding:** parse `Date` and `Time`, combine them into a timestamp, and convert measurement columns from text to numeric values after import
- **Merging / reshaping:** none -->

<!-- ## Beijing Multi-Site Air Quality

Webpage: <https://archive.ics.uci.edu/dataset/501/beijing+multi+site+air+quality+data>

```{r}
#| eval: false
beijing_air_quality <- fetch_ucirepo(id = 501)
beijing_air_quality_data <- beijing_air_quality$data$original

dim(beijing_air_quality_data)
head(beijing_air_quality_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** 420,768
- **Response variable:** a natural regression target is one pollutant such as `PM2.5`, `PM10`, or `O3`
- **Topic:** multi-site air-pollution and weather measurements in Beijing
- **Missing-data handling:** keep, drop, or impute rows with missing values; the UCI page states that missing data are denoted as `NA`
- **Parsing / encoding:** parse `year`, `month`, `day`, and `hour` into a timestamp
- **Merging / reshaping:** unzip and stack the multiple site files into one table, keeping `station` as a grouping variable if needed -->

<!-- ## SML2010

Webpage: <https://archive.ics.uci.edu/dataset/274/sml2010>

```{r}
#| eval: false
sml2010 <- fetch_ucirepo(id = 274)
sml2010_data <- sml2010$data$original

dim(sml2010_data)
head(sml2010_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** 4,137
- **Response variable:** a natural regression target is an indoor temperature variable such as the dining-room or room temperature
- **Topic:** smart-home environmental sensor measurements
- **Missing-data handling:** inspect and handle possible missing values; the UCI page says the dataset could contain missing values
- **Parsing / encoding:** parse the UTC `Date` and `Time` fields and skip the commented header lines that begin with `#`
- **Merging / reshaping:** combine `NEW-DATA-1.T15.txt` and `NEW-DATA-2.T15.txt` into one dataset -->

<!-- ## Online Retail II

Webpage: <https://archive.ics.uci.edu/dataset/502/online+retail+ii>

```{r}
#| eval: false
online_retail_ii <- fetch_ucirepo(id = 502)
online_retail_ii_data <- online_retail_ii$data$original

dim(online_retail_ii_data)
head(online_retail_ii_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** 1,067,371
- **Response variable:** a workable quantitative target is `UnitPrice` or an aggregated revenue outcome
- **Topic:** multi-year online retail transactions
- **Missing-data handling:** inspect and handle missing values, especially in customer-level fields
- **Parsing / encoding:** parse `InvoiceDate` as a date-time variable
- **Merging / reshaping:** combine the workbook sheets into one consistent transaction table before modeling -->

<!-- ## Open University Learning Analytics Dataset

Webpage: <https://archive.ics.uci.edu/dataset/349/open+university+learning+analytics+dataset>

```{r}
#| eval: false
oulad <- fetch_ucirepo(id = 349)
oulad_data <- oulad$data$original

dim(oulad_data)
head(oulad_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** not clearly specified on the UCI page
- **Response variable:** a workable quantitative target is assessment `score` after joining the student and assessment tables
- **Topic:** student activity, registration, and assessment behavior in online courses
- **Missing-data handling:** inspect and handle missing values; the UCI page marks the dataset as having missing values
- **Parsing / encoding:** convert date-like offset fields such as registration day, assessment day, and VLE interaction day into a consistent course-time scale
- **Merging / reshaping:** join the linked tables such as `studentAssessment.csv`, `studentInfo.csv`, `studentRegistration.csv`, `studentVle.csv`, and `vle.csv` -->

<!-- ## Restaurant & consumer data

Webpage: <https://archive.ics.uci.edu/dataset/232/restaurant+consumer+data>

```{r}
#| eval: false
restaurant_consumer <- fetch_ucirepo(id = 232)
restaurant_consumer_data <- restaurant_consumer$data$original

dim(restaurant_consumer_data)
head(restaurant_consumer_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** the main rating table has 1,161 user-place ratings; the auxiliary tables range from 130 to 2,339 rows
- **Response variable:** a clear regression target is `rating` from `rating_final.csv`
- **Topic:** restaurant recommendation with user, place, and context attributes
- **Missing-data handling:** inspect and handle missing values in files such as `geoplaces2.csv` and `userprofile.csv`
- **Parsing / encoding:** encode the many categorical preference and restaurant-description variables
- **Merging / reshaping:** join `rating_final.csv` with the user and restaurant tables using `userID` and `placeID` -->

## Communities and Crime Unnormalized

Webpage: <https://archive.ics.uci.edu/dataset/211/communities+and+crime+unnormalized>

```{r}
communities_crime <- fetch_ucirepo(id = 211)
communities_crime_data <- communities_crime$data$original

dim(communities_crime_data)
head(communities_crime_data)
```

- **Number of features:** 125
- **Number of targets:** 18 possible crime outcomes are described on the UCI page
- **Number of observations:** 2,215
- **Response variable:** a clear regression target is `ViolentCrimesPerPop`
- **Topic:** socio-economic, law-enforcement, and crime measurements for U.S. communities
- **Missing-data handling:** inspect and handle the many missing values, especially in the law-enforcement variables
- **Parsing / encoding:** encode categorical identifiers such as `State` if they are retained
- **Other preparation:** choose one crime variable as the target and remove overlapping crime subtotal variables that would leak information into that target

<!-- ## KDD Cup 1998

Webpage: <https://archive.ics.uci.edu/dataset/129/kdd+cup+1998>

```{r}
#| eval: false
kdd_cup_1998 <- fetch_ucirepo(id = 129)
kdd_cup_1998_data <- kdd_cup_1998$data$original

dim(kdd_cup_1998_data)
head(kdd_cup_1998_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** not clearly specified on the UCI page
- **Number of observations:** 191,779
- **Response variable:** a clear regression target is `TARGET_D`, the donation amount in the original KDD target files
- **Topic:** direct-marketing donation modeling
- **Missing-data handling:** inspect and handle the missing values noted on the UCI page
- **Parsing / encoding:** encode the large number of categorical marketing and demographic variables
- **Merging / reshaping:** join the learning file with the provided target file information when reconstructing a modeling table -->

## Real Estate Valuation

Webpage: <https://archive.ics.uci.edu/dataset/477/real+estate+valuation+data+set>

```{r}
real_estate <- fetch_ucirepo(id = 477)
real_estate_data <- real_estate$data$original

dim(real_estate_data)
head(real_estate_data)
```

- **Number of features:** 6
- **Number of targets:** 1
- **Number of observations:** 414
- **Response variable:** `Y house price of unit area`
- **Topic:** housing valuation in New Taipei City
- **Parsing / encoding:** convert `X1 transaction date` from its decimal-year format into a more interpretable time representation if needed

<!-- ## UJIIndoorLoc

Webpage: <https://archive.ics.uci.edu/dataset/310/ujiindoorloc>

```{r}
#| eval: false
ujiindoorloc <- fetch_ucirepo(id = 310)
ujiindoorloc_data <- ujiindoorloc$data$original

dim(ujiindoorloc_data)
head(ujiindoorloc_data)
```

- **Number of features:** not clearly specified on the UCI page
- **Number of targets:** 4 position-related outputs are described on the UCI page
- **Number of observations:** 21,048 total, from 19,937 training rows and 1,111 validation rows
- **Response variable:** for regression, the clearest targets are `Longitude` and `Latitude`
- **Topic:** indoor localization from WiFi fingerprints
- **Missing-data handling:** none indicated on the UCI page, but the value `100` should be treated as a special code for undetected WAPs rather than as an ordinary numeric signal
- **Parsing / encoding:** parse the UNIX `Timestamp` if time effects matter and decide how to treat categorical fields such as `BuildingID`, `SpaceID`, `UserID`, and `PhoneID`
- **Merging / reshaping:** combine `trainingData.csv` and `validationData.csv` if you want one unified analysis table -->

# Final remark

A few of the datasets above are more naturally classification datasets, but they were included because they were in your earlier long list. If you want, I can also make a **strict version** that keeps only datasets that clearly satisfy all of your regression-project rules without any caveats.
